Forecasting the power of Higher Order Weak Lensing Statistics with automatically differentiable simulations

### 2022-02-14 paper/paper.tex
Updates from Overleaf

To understand how accurate our simulations are, and to validate the choice of the smoothing size to apply, we tried to reproduce the summary statistics from the only Dark $\kappa-TNG$ simulations. 
 We show the results from the angular power spectrum comparison for 3 source redshifts in Figure \ref{fig:ps_comp}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{paper/figures/clshalofit_comp.png}
    \caption{
    \textbf{Upper panel}: Angular power spectra for 3 different source redshifts from
our DLL maps. \textbf{Lower panel}: Fractional differences between the
DLL and Halofit power spectra for 3 source redshifts. The power spectra and ratios are means over 100 map realisations. The two vertical lines define the range of $\ell$ between $[300,3000]$.}
    \label{fig:ps_comp}
\end{figure}
% with a smoothing size $\theta=3.6$. We perform the angular power spectrum analysis in a range of $\ell=[300,3000]$ according to the requirement specified in  \cite{mandelbaum2018lsst}.

>>>>

To understand how accurate our simulations are, and to validate the choice of the smoothing size to apply, we tried to reproduce the summary statistics from the only Dark $\kappa$TNG simulations. 
 We show the results from the angular power spectrum comparison for 3 source redshifts in Figure \ref{fig:clsratktng_comp1arc}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{paper/figures/clsratktng_comp1arc.png}
    \caption{
The fractional differences of the DLL power spectra with respect to the $\kappa$TNG predictions for 3 source redshifts.
 The power spectra means over 100 map realisations. The maps are smoothed with a 1 arcmin Gaussian filter. The shaded regions represent the standard deviation from 1000 $\kappa$TNG realisations.}
    \label{fig:clsratktng_comp1arc}
\end{figure}
% with a smoothing size $\theta=3.6$. We perform the angular power spectrum analysis in a range of $\ell=[300,3000]$ according to the requirement specified in  \cite{mandelbaum2018lsst}.
